Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-27 latex/comp_or.tex
Running iRace

%The testing experiments are performed on a 64-bit, 16GiB, 3.2GHz, 8-core processor, 2 threads per core, AMD FX-8320E, with {\it Linux Ubuntu 22.04} as the operational system and {\it Python 3.10.4}\/ as the programming language.

@@

@@

>>>>

@@

A relevant problem with meta-heuristics is the parameter's adjustment to extract the best possible efficiency in the optimization. The bulk of the tools to fine-tune these parameters utilize a statistical backdrop that enables them to make accurate predictions regarding the differences in candidate configurations' performance. Inadequacies in the design of the statistical experiment may therefore lead to erroneous results from the statistical tests and, subsequently, cause the approach to produce inaccurate comparisons of candidate configurations. That is why all parameters were set using the $iRace$ package \citep{LopezIbanezManuel2016}. Supplying $iRace$ with a range for $volThreshold$ as [0.80 to 0.99], {\it iRace} yielded ....., by training on the uneven instances numbers.

@@

	Another important contribution is that we employed the {\it iRace} package to fine tune the meta-heuristics parameters, guaranteeing the best possible performance for the instances under training and testing.
